Appendix S1: Supporting Tables and Figures

### 2022-04-18 ms/SI.Rmd
Update MS
As per editor comments

# Load functions and variables only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

@@

### **`r s_table("corr")`**

@@

@@

Model fit as measured with conditional Akaike Information Criterion (cAIC). Environmental models included the effects of temperature, precipitation, precipitation seasonality, and area. Reproductive models included the effects of % apomictic taxa, precipitation, precipitation seasonality, and area. Lower cAIC indicates better fit.

@@

```{r grain-size, fig.width = 7, fig.height = 3}
# Helper function to format resolution labels
km_lab <- function (x) {
  as.numeric(x) %>% 
    scales::number(suffix = "km", scale = 1e-3)
}

@@

# Percent of grid cells with redundancy > 0.5 by grain size
a <- ggplot(redundancy_summary, aes(x = res, y = percent_above_50)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy > 0.5"
  )

# Percent of grid cells with redundancy = 0 by grain size
b <- ggplot(redundancy_summary, aes(x = res, y = percent_singletons)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy = 0"
  )

@@

(A) Raw taxonomic diversity, (B) phylogenetic diversity, and (C) functional diversity of the ferns of Japan plotted by latitude. For (B) and (C), raw branchlengths were transformed to relative values by dividing each branchlength by the sum of all branchlengths. Trendlines fit with general additive model using `r func("geom_smooth")` function in the `r pack("ggplot2")` R package [@Wickham2016].

@@

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleo-endemism), restricted data set including only taxa endemic to Japan. 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Materials and Methods.

@@

Relationship between (A) phylogenetic diversity (PD) and (B) relative PD and % apomictic taxa, models inferred using phylogeny with branchlengths in units of expected genetic change (untransformed ML tree). Ribbon shows 95% confidence interval of model. Line fit with the focal predictor variable while averaging over other predictors. For RPD, the standard effect size (SES) was calculated by comparing raw values to a null distribution of 999 random values, and significance (*P*-value) calculated using a two-tailed test (see Materials and Methods).

>>>>

# Load functions and variables only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE, dev="cairo_pdf")
```

@@

\clearpage
### **`r s_table("corr")`**

@@

@@

Model fit as measured with conditional Akaike information criterion (cAIC). Environmental models included the effects of temperature, precipitation, precipitation seasonality, and area. Reproductive models included the effects of % apomictic taxa, precipitation, precipitation seasonality, and area. Lower cAIC indicates better fit.

@@

@@

```{r grain-size, fig.width = 7, fig.height = 3}
# Helper function to format resolution labels
km_lab <- function (x) {
  as.numeric(x) %>% 
    scales::number(suffix = "", scale = 1e-3)
}

@@

# Percent of grid cells with redundancy > 0.5 by grain size
a <- ggplot(redundancy_summary, aes(x = res, y = percent_above_50)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution (km)",
    y = "Redundancy > 0.5"
  )

# Percent of grid cells with redundancy = 0 by grain size
b <- ggplot(redundancy_summary, aes(x = res, y = percent_singletons)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution (km)",
    y = "Redundancy = 0"
  )

@@

(A) Raw taxonomic diversity, (B) phylogenetic diversity, and (C) functional diversity of the ferns of Japan plotted by latitude. For (B) and (C), raw branch lengths were transformed to relative values by dividing each branchlength by the sum of all branch lengths. Trendlines fit with general additive model using `r func("geom_smooth")` function in the `r pack("ggplot2")` R package [@Wickham2016].

@@

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleoendemism), restricted data set including only taxa endemic to Japan. 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Materials and Methods.

@@

Relationship between (A) phylogenetic diversity (PD) and (B) relative PD and % apomictic taxa, models inferred using phylogeny with branch lengths in units of expected genetic change (untransformed ML tree). Ribbon shows 95% confidence interval of model. Line fit with the focal predictor variable while averaging over other predictors. For RPD, the standard effect size (SES) was calculated by comparing raw values to a null distribution of 999 random values, and significance (*P*-value) calculated using a two-tailed test (see Materials and Methods).
